### 2015-12-29 extended-abstract.tex
finish text to submit to InsTED

\vskip.2in
Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers (TTBs) on a not-infrequent basis (Bown 2011). A significant literature has explored the question of which industries receive protection through TTBs and under what conditions this happens. This project asks a related but distinct question: given that a product receives protection, what determines the duration of the protection it receives? \\

@@

This uncertainty may derive from several sources. The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a TTB. Indirectly, this may reflect the ITC's preferences about the costs of disputes and retaliation by trade partners. Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to consumers and trading relations. This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question. \\

An important question in this model is why an industry that receives protection as a result of the original interaction concerning the imposition of the TTB would fail to get it renewed. At the most basic level, if we assume the industry faces the same uncertainty and responds in the same way, it could get a different draw and thus a different outcome. In addition, having the level of the TTB set by the original interaction serves to reduce the industry's incentive to exert effort on the margin. \\

@@

\vskip.5in
\begin{itemize}
	\item Even if AD economic conditions can't be measured / don't bind, doesn't mean that real economic conditions don't play into ITC's decision-making process
	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
\end{itemize}

\vskip.3in
Chad and Maurizio Zanardi are working on a paper on AD 5-year reviews
\begin{itemize}
	\item They have the data, but are not exploiting cross-industry variation
		\begin{itemize}
			\item Instead, aggregate variation, things like recessions, exchange rates
		\end{itemize}
	\item They don't have a theory for the cross-industry variation, because the economic determinants are meaningless after five years
	\item Politics could be that theory (my theory from above)		
\end{itemize}

>>>>

\vskip.2in
Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers (TTBs) on a not-infrequent basis (Bown 2011\footnote{Bown, Chad P., ``Taking Stock of Antidumping, Safeguards and Countervailing Duties, 1990-2009,'' The World Economy v34, n12 (December 2011): 1955-1998.}). A significant literature has explored the question of which industries receive protection through TTBs and under what conditions this happens. This project asks a related but distinct question: given that a product receives protection, what determines the duration of the protection it receives? \\

@@

There are several possible sources of this uncertainty. The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a TTB. Indirectly, this may reflect the ITC's preferences about the costs of disputes and retaliation by trade partners. Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to consumers and trading relations. This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question. \\

An important question in this model is why an industry that receives protection as a result of the original interaction concerning the imposition of the TTB would fail to get it renewed. At the most basic level, if we assume the industry faces the same uncertainty and responds in the same way, it could get a different draw and thus a different outcome. Moreover, having the level of the TTB set by the original interaction serves to reduce the industry's incentive to exert effort on the margin. \\

@@

Another interesting dimension along which there is uncertainty for the ITC is in its evaluation of the probability with which trading partners will dispute or retaliate against a TTB. This not only varies across TTBs, but may vary across time. In particular, the ITC can observe whether a dispute has been filed during the first five years of a TTB and update its beliefs about future retaliation in a way that varies across industries. \\

There is much to be learned about the workings of the world trading system by examining the duration of deviations from base tariff commitments. I plan a project whose first stage is theoretical with a second, later stage in which the theory is tested on a data set of renewal decisions for anti-dumping measures.
